Discrete Quantum Theories and Computing

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex

\date{\today}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Classical $\frac{1}{4}$-deterministic Probability Measure}

Although the definition of $\delta$-determinism in our paper only
applied on QIVPMs~\cite{THOS2017}, this definition can be easily
extended to apply on both classical and quantum IVPMs as follow.

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
is a QIVPM and $\events'$ is the set of mutually commuting events,
$\eventsC$, when $\bar{\mu}$ is a classical one. $\bar{\mu}$ is
$\delta$-deterministic if, for every event $P\in\events'$, we have
that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Example $\frac{1}{4}$-deterministic classical
IVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ on
commuting events $P$.}
\begin{tabular}{cccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$  & $\bar{\mu}_{C}(P)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$  & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$  & $\left[\frac{3}{4},1\right]$\tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$  & $\left[1,\frac{1}{4}\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$  & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\end{table}

Then, it is easy to construct $\frac{1}{4}$-deterministic classical
IVPMs~$\bar{\mu}_{A}$, $\bar{\mu}_{B}$ and $\bar{\mu}_{C}$ defined
in Table~\ref{tab:classical-IVPMs}.

\noindent This definition puts no restrictions on the set of intervals
itself, only on which intervals are assigned to events. When
$\delta=0$, every event must be assigned a probability either in
$\imposs$ or in $\necess$, i.e., every event is completely determined
with certainty. As $\delta$ gets larger, the QIVPM allows for more
indeterminate behavior. 
For example, $\bar{\mu}_{A}$ defined in
Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
$\imposs\subseteq\left[0,0\right]$ and
$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
$\bar{\mu}_{A}$ is still not $\frac{1}{3}$-deterministic because
$\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
$\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally,
when $\delta=1$, because every interval is a subset of $\unknown$,
every QIVPM is $1$-deterministic. In particular, the non-informative
QIVPM~$\bar{\mu}_{A}$ is 1-deterministic.

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Response of the Referee Report of ``Quantum Interval-Valued Probability:
Contextuality and the Born Rule''}

@@

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Classical $\frac{1}{4}$-deterministic Probability Measure}

Although the definition of $\delta$-determinism in our paper only
applied on QIVPMs~\cite{THOS2017}, this definition can be easily
extended to apply on both classical and quantum IVPMs as follow.

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
is a QIVPM and $\events'$ is the set of mutually commuting events,
$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
is $\delta$-deterministic if, for every event $P\in\events'$, we
have that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent Then, it is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always lands on head. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how a coin close to
double-headed, which we can certainly know the outcome of an coin
even before tossing. We see here that we can construct $0$-deterministic
as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
classical probability measure. BUT the situation changes in the quantum
case, WE CANNOT construct $\delta$-deterministic probability measures
for $\delta$ that are less than $\frac{1}{3}$.

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent Then, it is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always lands on head. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how a coin close to
double-headed, which we can certainly know the outcome of an coin
even before tossing. We see here that we can construct $0$-deterministic
as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
classical probability measure. BUT the situation changes in the quantum
case, WE CANNOT construct $\delta$-deterministic probability measures
for $\delta$ that are less than $\frac{1}{3}$.

\paragraph{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is
Impossible}

To illustrate our proof for non-existence of $\delta$-deterministic
QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
\[
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
\end{cases}
\]
However, since we know that $0$-deterministic QIVPMs do not exist,
the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
is indeed a $0$-deterministic QIVPM.

by checking that for orthogonal projectors~$P_{0}$ and $P_{1}$,
we have that $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\cite{TaiThesis2018}.
Indeed when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

\begin{figure}

\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$.}

\end{figure}

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex

\author{Amr Sabry}
\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\date{\today}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classical $\frac{1}{4}$-deterministic Probability Measure}

@@

Although the definition of $\delta$-determinism in our paper only
applied on QIVPMs~\cite{THOS2017}, this definition can be easily
extended to apply on both classical and quantum IVPMs as follow.

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
is a QIVPM and $\events'$ is the set of mutually commuting events,
$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
is $\delta$-deterministic if, for every event $P\in\events'$, we
have that either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent Then, it is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always lands on head. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how a coin close to
double-headed, which we can certainly know the outcome of an coin
even before tossing. We see here that we can construct $0$-deterministic
as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
classical probability measure. BUT the situation changes in the quantum
case, WE CANNOT construct $\delta$-deterministic probability measures
for $\delta<\frac{1}{3}$.

\subsection{Why a Quantum $\frac{1}{4}$-deterministic Probability Measure is
Impossible}

To illustrate our proof for non-existence of $\delta$-deterministic
QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
\end{cases}
\end{equation}
However, since we know that $0$-deterministic QIVPMs do not exist,
the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
is indeed a QIVPM. Since the range of $\bar{\mu}^{\textrm{D}}$, $\left\{ \imposs,\necess\right\} $,
is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
that for orthogonal projectors~$P_{0}$ and $P_{1}$, 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
\end{equation}
then we can apply the same reason of proving classical inclusion-exclusion
principle~\cite{TaiThesis2018} to get
\[
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)
\]
which implies $\bar{\mu}^{\textrm{D}}$ is convex, i.e., $\bar{\mu}^{\textrm{D}}$
is a QIVPM. Therefore, our task now is to prove Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).

\begin{figure*}
\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$.}
\end{figure*}
For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
$\bar{\mu}\left(P_{0}\right)\subseteq\left[\frac{3}{4},1\right]$,
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$,
and $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},\frac{5}{4}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.

For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Response to the Referee Report of ``Quantum Interval-Valued Probability:
Contextuality and the Born Rule''}

\author{Yu-Tsung Tai}

\affiliation{Department of Mathematics, Indiana University, Bloomington, Indiana
47405, USA}

\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\author{Andrew J. Hanson}

\affiliation{Department of Informatics, Indiana University, Bloomington, Indiana
47405, USA}

\author{Gerardo Ortiz}

\affiliation{Department of Physics, Indiana University, Bloomington, Indiana 47405,
USA}

\author{Amr Sabry}

\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

@@

\date{\today}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Classical \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability
Measure}

@@

Although the definition of $\delta$-determinism in our paper only
applied on QIVPMs~\cite{THOS2017}, this definition can be easily
extended to apply on both classical and quantum IVPMs as follow.

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
is a QIVPM and $\events'$ is the set of mutually commuting events,
$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
is $\delta$-deterministic if, for every event $P\in\events'$, we
have either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

@@

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent It is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always lands on head. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how a coin close to
double-headed, which we can certainly know the outcome of an coin
even before tossing. We see here that we can construct $0$-deterministic
as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
classical probability measure. BUT the situation changes in the quantum
case, WE CANNOT construct $\delta$-deterministic probability measures
for $\delta<\frac{1}{3}$.

\section{Why a Quantum \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability Measure is
Impossible}

### 2018-01-25 prop_prop_letter_ajhs_referee_response.tex

\date{\today}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Classical \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Probability
Measure}

Although the definition of $\delta$-determinism in our paper only
applied to QIVPMs~\cite{THOS2017}, this definition can be easily
extended to apply to both classical and quantum IVPMs as follow.

@@

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
is a QIVPM and $\events'$ is the set of mutually commuting events,
$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
is $\delta$-deterministic if, for every event $P\in\events'$, we
have either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent It is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always comes up heads. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how close a coin is
to double-headed, which we can certainly know the outcome of a coin
even before tossing. We see here that we can construct $0$-deterministic
as well as $\frac{1}{4}$-deterministic and in fact for any $\delta$
in the range $\left[0,1\right]$ we can construct a $\delta$-deterministic
classical probability measure. BUT the situation changes in the quantum
case, WE CANNOT construct $\delta$-deterministic probability measures
for $\delta<\frac{1}{3}$.
